\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-04-30 reviews/response.Rmd

---
title: Response to reviewers
author: JCGS-18-293
output:
  MonashEBSTemplates::memo:
    includes:
      in_header: preamble2.tex
fontfamily: mathpazo
---

We thank the reviewers for their helpful feedback which has led to many improvements in the paper. The point by point description of changes are below: the reviewers' comments are in red and our response is in black.

In addition, we have expanded the paper by adding a short section titled "3. A fully-fledged faceting calendar method" which describes a new function `facet_calendar()`, that extends **ggplot2** intervals and complements the existing function `frame_calendar()`. It allows this algorithm to integrate more deeply with the **ggplot2** architecture.

@@

# Reviewer 1 comments {-}

> Figure 2 and Figure 10 show much the same information. You can see the Australian Open period in both. There is more detail in Figure 10 for the State Library.  The gaps in the Birrarung Marr data are easier to see in Figure 2.

We have explained the purpose of showing both displays in the revised paper, by adding a new subsection "2.4 Reasons to use calendar-based graphics" to explain why to use calendar plots, and what information is typically revealed by calendar plots but not by other plots. The calendar display doesn't replace traditional displays, but serves to complement to further tease out interesting structures in the data.

@@

> Figure 11 is not described well.  What does the V-pattern mean?  How can you see the strong autocorrelation at weekends?  There are only dots.

We have changed the explanation of Fig 11 to make it clearer. In the revised paper this is now Fig 10. The V pattern is due to morning and evening commuter pattern on weekdays. We realised that the daily lag relationshsips would be read more easily if local scale was used, that is, each day is scaled relative to itself. This has been done, and the different autocorrelation pattern for week days and weekends is now clearer.

@@

> The colours are not well chosen in Figure 15.  It is hard to see the averages for households 1 and 3.

Colours have been changed to make it clearer.

> There are too many large plots in the paper.  Figure 6 is not needed and Figure 12 is not needed.

We are not sure if you mean Fig 6 here. Fig 6 is the diagram illustrating the yearly layout, and we think it is important to keep this illustration in the paper. On Fig 12, we think you mean Fig 13 is not necessary along with Fig 12. We have kept Fig 13 with the Chinese labels, to illustrate variety in language labels as well as the examination of variability using boxplots.

> How do you know that the New Year's Eve outliers in Figure 12 are from the same sensor?  That is not in the plot.

Yes, you are correct. You can't see that it is one sensor from this plot. The explanation of Fig 12 (now 11) focuses on the variability of counts across days, instead of outliers.

@@

> Do Figures 16-19 show much?  Drawing all four series as rows in facets one above the other would show the holidays better.  Comparisons of the households would be easier.  The six-weeks months confuse looking at holidays.  What are the one-day peaks in the middle of holidays?

Yes, we agree, they take up too much space. But the message of comparing multiple households is good to illustrate the benefits of the calendar plots, so we have reduced the plots to focus only on Jan-June 2018 and show all four households in one plot.

@@

> There is a shiny app that presents some of the data.  It is not well described.  The plot at lower left is cumulative precipitation for each month, but it does not say so.  Why is cumulative precipitation by month interesting?  Months are of different lengths.  You can select single days in the time series.  Can you select more than one day?

We have added a text box underneath the plots in the shiny app. To describe the app in this paper would be too distracting for the reader. Cumulating monthly precip provides a more interesting look at rainfall, and it approximates how the NY Times displays weather. Only one day can be selected.

@@

# Reviewer 2 comments {-}

> p.10, l.1-15 It wasn't clear to me why the subtraction was performed in the equation (2) because I couldn't find any description for the global coordinate system of the canvas. The value of y could be negative. Please add the description how to deal with the coordinate system, especially the y-axis.

This is already explained directly after the equation. It is because plots are measured from top left of the display area, which is the common computer graphics standard.

@@

# Reviewer 3 comments {-}

Thank you for carefully reading of our paper.

> p1, l32: "information, and events." - remove the comma (and all of the other similar small details)

Fixed in multiple places. The language in many places has been modified according to these comments.

@@

> p2, l9: "grammar of graphics" - provide reference immediately here and not only later in the article and explain what the grammar of graphics is; also "piped into" may not be understood by outsiders

Done.

> Fig.1 (& related figs): I suppose you use a "3-class Dark2" color scheme from Rcolorbrewer? This does not work well when printed in gray scale: The colors become almost indistinguishable. ...

We have changed the colour scheme from ColorBrewer palette "Dark2" to "4-class PuOr" in Figure 1 and related figures. This works better on the grey background, but still can be read on a white background in the other plots.

@@

> Fig.4: Colors orange & purple are hard to distinguish in grayscale. Moreover, you should use different colors here as these 2 colors are already related to the 3 stations.

In Fig 4, we have changed the colour to red and blue picked from a ColorBrewer "4-class RdYlBu" colour scheme. Fig 1-3 colours used for the 3 stations use a different palette.

@@

> Fig.2: Can you match the minor grid lines with the start of a month, rather than the middle of a month? This will make it much easier to identify the approximate dates for some of the other spikes. No need to label these minor grid lines.

Done.

> Fig.2: You mention "small multiples" only in a figure caption. This concept is a central
part of your calendar graphics and should be summarized in more details (including references) in the main text. Also mention Unwin & Valero-Mora's "Ensemble Graphics", JCGS, 27(1), as a major concept that applies to both sets of related figures in your article.

We have explained the idea of faceting and also referred to small multiples, trellis charts, and ensemble graphics in the text now, at the end of the second paragraph in Introduction section.

@@

> Fig.4: Colors orange & purple are hard to distinguish in grayscale. Moreover, you should use different colors here as these 2 colors are already related to the 3 stations.

Done.

> Fig.4: Prior to reading the text on p8, I was really confused and even assumed there was a major bug in your R code. Having 2 days in early May and 1 day in early Oct, then 3 days missing, and then the remainder of the month is really confusing for someone who only looks at the figure without reading the text in detail. At least mention this layout anomaly in the figure caption.

Thanks. I have pointed out the layout anomalies for May and October in the Figure 4  (now 6) caption.

@@

> p8, l19: "wrap the last few days up to the top row of the block": This answers
my comment for Fig.4 now, but this layout still remains misleading. We expect to
see some similar temporal pattern in nearby graphs. But there could be considerable differences over a 30-day period, e.g., in your example from Section 3:
What if these 1 or 2 days are after some summer vacation with lots of air conditioning
use, but the vacation already started in the previous month and continued through the middle of the current month. Suddenly, there will be a few huge spikes that interrupt
the overall low-energy pattern. I could think of 2 possible solutions:
(i) Add a 6th week for each month; or (ii) Add the extra days to the
start of the next month. This is sometimes called a
"Calendar Heatmap Tetris Chart", see for example https://stackoverflow.com/questions/27000131/calendar-heat-map-tetris-chart
[both of these features could become additional user options for your R function]

It is intentional to conform a calendar layout of 5 rows and 7 columns for the purpose of compactness. Only one or two months in a year will span over 6 weeks, which would result in more unused space for a year-long calendar plot. We don't shift the extra days to the next month because it is difficult for readers to distinguish which month contains these additional days without proper labelling. We agree that it is disruptive since time is usually perceived as linear, but it is also a common calendar convention.

@@

> p13, l39: "Figure 13 shows the same plot as Figure 12 labelled": You can't jump forward to a figure before all intermediate figures have been introduced. The previous fig was Fig.8. Figs 9-11 have not been mentioned yet. Either rearrange your figures so that 12-13 become 9-10, or use Chinese characters for one of the previously introduced figs (1-8).

Fixed. "Figure 13 shows the same plot as Figure 12 labelled" is deleted.

> p13, possible subsection 2.2.6: You seem to have a "sunday = FALSE" default. If TRUE, does this make Sunday the start of the week (as used in the US & Canada)? If so, mention this as an option. No need for a figure.

Done. We deprecated argument `sunday` in favor of `week_start` that is more general. We added a new subsection on "Start of the week" to briefly explain the option. We have reorganized the order of the subsections to be consistent with the function argument's ordering.

@@

> p13, possible subsection 2.2.7: How can you enter specific holidays? These are different from country to country, e.g., based on national holidays such as Thanksgiving, Labor Day, independence days, religious holidays, etc.

We used `tsibble::holiday_aus()` for generating Australian public holidays, prior to creating calendar displays. Whether to use holidays or not is a data-specific problem, and would depend on local analysts incorporating a holiday calculator into their country specific analyses. This is beyond the scope of this paper.

@@

> Fig.8: "impossible to compare the size of peaks between days." - Correct; since this is based on ggplot, could you use colors from a sequential color scheme that maps the counts, e.g., from faint yellow (0) to dark red (for the overall max)? This might be another
useful argument for a future extension of your function.

We recommend against this idea. The better approach is to re-make the plot with global scaling to focus on counts. No need to make one plot show everything possible, but more confuding, better to make multiple plots.

### 2019-04-30 main.Rmd
remove boxplots in english from the paper

The algorithm can also produce more complicated plots, such as boxplots. Figure \@ref(fig:boxplot) uses a loess smooth line [@cleveland1979loess] superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. The last week of December is the holiday season: people are off work on the day before Christmas (December 24), go shopping on the Boxing day (December 26), and stay out for the fireworks on New Year's Eve.

```{r boxplot, fig.height = 8, fig.cap = "Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased varibility is noted on the last day of December as approaching towards New Year's Eve."}
```

@@

(ref:chn-cap) The same plot as Figure \@ref(fig:boxplot), but with the month and week day labels in Chinese. It demonstrates the natural support for languages other than English.

>>>>

The algorithm can also produce more complicated plots, such as boxplots. Figure \@ref(fig:chn) uses a loess smooth line [@cleveland1979loess] superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. The last week of December is the holiday season: people are off work on the day before Christmas (December 24), go shopping on the Boxing day (December 26), and stay out for the fireworks on New Year's Eve. The text in the plot is labeled in Chinese, showcasing the support for other languages.

```{r boxplot, fig.height = 8, fig.cap = "Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased varibility is noted on the last day of December as approaching towards New Year's Eve.", fig.show = "hide"}
```

@@

(ref:chn-cap) Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased variability is noted on the last day of December as approaching towards New Year's Eve. The month and week day are labeled in Chinese, which demonstrates the natural support for languages other than English.

### 2019-04-30 main.tex
remove boxplots in english from the paper

The algorithm can also produce more complicated plots, such as boxplots. Figure \ref{fig:boxplot} uses a loess smooth line \citep{cleveland1979loess} superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. The last week of December is the holiday season: people are off work on the day before Christmas (December 24), go shopping on the Boxing day (December 26), and stay out for the fireworks on New Year's Eve.

{\centering \includegraphics[width=\textwidth]{figure/boxplot-1}

\caption{Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased varibility is noted on the last day of December as approaching towards New Year's Eve.}\label{fig:boxplot}
\end{figure}

@@

\caption{The same plot as Figure \ref{fig:boxplot}, but with the month and week day labels in Chinese. It demonstrates the natural support for languages other than English.}\label{fig:chn}
\end{figure}

>>>>

The algorithm can also produce more complicated plots, such as boxplots. Figure \ref{fig:chn} uses a loess smooth line \citep{cleveland1979loess} superimposed on side-by-side boxplots. It shows the distribution of hourly counts across all 43 sensors during December. The last week of December is the holiday season: people are off work on the day before Christmas (December 24), go shopping on the Boxing day (December 26), and stay out for the fireworks on New Year's Eve. The text in the plot is labeled in Chinese, showcasing the support for other languages.

@@

\caption{Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased variability is noted on the last day of December as approaching towards New Year's Eve. The month and week day are labeled in Chinese, which demonstrates the natural support for languages other than English.}\label{fig:chn}
\end{figure}
